The Astropy Project

### 2017-11-10 main.tex
remove comment
units draft

We start by describing the way the \astropy project works and is
organized in \sectionname~\ref{sec:concepts}.  The project develops a core
package called \astropypkg (\sectionname~\ref{sec:core}) and several
separate packages that help setting up the infrastructure for testing,
documentation etc.\ (\sectionname~\ref{sec:infrastructure}).
We end with a short vision for
the future of \astropy in particular and astronomical software in general
in \sectionname~\ref{sec:future}.

\section{Major concepts}
\label{sec:concepts}

@@

\subsection{Use of Quantities across package}
% Marten and Tom R.

{\bf Very rough first text!}

Historically, it has been unusual to keep units as part of numbers, especially as speed was often deemed essential and quantities used to be slower than regular arrays. Hence, programs and functions expected to be fed parameters in particular units, as (hopefully) stated in their documentation.  In \astropypkg~0.4, therefore, unit and quantity support was still somewhat spotty, but this has changed greatly.  One of the riskiest classes was angles, where both degrees and radians were ``obvious'' default units to some. As a consequence, quantities are most fully integrated in the coordinates module (\sectionname~\ref{sec:coordinates}). In \astropypkg~2.0, one can also opt in to use quantities fully in tables, by using the {\tt QTable} class (see \sectionname~\ref{sec:table}). As a result, units in FITS tables are also well-supported. For most other modules, quantities are at least accepted, and often assumed by default.

In the process, some standard wrappers have been defined that make defining functions that require quantities as input simpler. As an extension of this, we plan to define wrappers for functions that work on numbers that will automatically convert quantities to any required units.

@@

% \subsection{Analytic Functions}
% moved to models and depreciated --
% just here for completeness at the moment
\inlinecomment{BMS}{I suggest to order the subsection lexicographically as reading the draft the current order seemed very random (unlike at the docs page where they the grouping logic is obvious)}
\subsection{Units and quantities}
\label{sec:units}
\inlinecomment{Marten, Adrian}{}

The \package{Units} and \package{Quantities} packages were described in detail in \cite{astropy}.

%\subsubsection{Key new features}

%\begin{description}
%    \item[Speed improvements] ...
%    \item[Logarithmic units and magnitudes] ...
%    \item[Interaction with \package{numpy} arrays] ...
%\end{description}

@@

%\section{Learning Astropy}
%\label{sec:learning}
% Kelle, Adrian
%\inlinecomment{BMS}{would astropy learn mature enough to described in the paper, or maybe it should go as a subsection for the next, future of astropy section?}

%Explain components: Documentation, Tutorials, and lessons

>>>>

We start by describing the way the \astropy project works and is
organized in \sectionname~\ref{sec:org}.  The project develops a core
package called \astropypkg (\sectionname~\ref{sec:core}) and several
separate packages that help setting up the infrastructure for testing,
documentation etc.\ (\sectionname~\ref{sec:infrastructure}).
We end with a short vision for
the future of \astropy in particular and astronomical software in general
in \sectionname~\ref{sec:future}.

\section{Organization and infrastructure}
\label{sec:org}

@@

@@

% \subsection{Analytic Functions}
% moved to models and depreciated --
% just here for completeness at the moment
\inlinecomment{BMS}{I suggest to order the subsection lexicographically as reading the draft the current order seemed very random (unlike at the docs page where they the grouping logic is obvious)}

\subsection{Units and quantities}\label{sec:units}
% Adrian, Marten

% TODO: should this just be called "Units"? all other sections in here look like
% they are named by the subpackage name -- quantity is an object within the
% package

The \texttt{astropy.units} subpackage adds support for representing units and
numbers with associated units (``quantities'') in code.
Historically, quantities in code have often been represented simply as numbers,
with units implied or noted via comments in the code because of considerations
about speed: having units associated with numbers inherently adds overhead to
numerical operations.
In \texttt{astropy.units}, \texttt{Quantity} objects subclass the \texttt{numpy}
array object and has been designed with speed in mind.
As of \astropypkg version 2.0, units and quantities are prevalent in most other
\astropypkg subpackages and are thus a key concept for using the package as a
whole.
The motivation and key concepts behind this subpackage were described in detail
in the previous paper \citep{astropy}, and thus here we primarily highlight new
features and improvements.

\begin{description}
    \item[Speed improvements] ...
    \item[Logarithmic units and magnitudes] ...
    \item[Using quantities in tables] In \astropypkg~2.0, one can also opt in to
        use quantities fully in tables, by using the {\tt QTable} class (see
        \sectionname~\ref{sec:table}). As a result, units in FITS tables are also
        well-supported. For most other modules, quantities are at least
        accepted, and often assumed by default.
    \item[Defining functions that require quantities] In the process, some
        standard wrappers have been defined that make defining functions that
        require quantities as input simpler. As an extension of this, we plan to
        define wrappers for functions that work on numbers that will
        automatically convert quantities to any required units.
    \item[Interaction with \package{numpy} arrays] ...
\end{description}

@@
